---
title: "report_tm"
author: "Yanjin Li"
date: "12/11/2016"
output: pdf_document
---

```{r setup, include=FALSE}
# Load packages
library(dplyr)
library(DBI)
library(tidyr)
# For text mining
library(NLP)
library(tm)
library(SnowballC)
library(ggplot2); theme_set(theme_bw())

dat.scripts <- readRDS("/Users/yanjin1993/GitHub/ADA.Simpson.textmining-/data/dat_scripts.rds")
```

## Section #: Text Mining Procedures 

Start by saving your text files in a folder titled: “texts” This will be the “corpus” (body) of texts you are mining. Here, we can inspect contents of the corpus we just generated. 

```{r, echo=TRUE}
# convert multibyte to bibyte   
dat.scripts$spoken_words <- iconv(enc2utf8(dat.scripts$spoken_words),sub="byte")
dat.scripts$word_count <- ifelse(!is.na(dat.scripts$word_count), as.numeric(dat.scripts$word_count), 0)

# tansform script text lines into corpus (separated text files)
myCorpus <- Corpus(VectorSource(dat.scripts$spoken_words))
# check original text data's meta-data
inspect(myCorpus[1])
```

Once all corpus files prepared, text mining process can be initiated. We will present a text mining example along with explanations to the text mining procedures. The original text:

> \textit{What does your phrase "17 pieces of Tahitian South Sea pearl" mean? I am very interested in this necklace - is this your best price?}


  ### Convert to lowercase:
```{r}
myCorpus <- tm_map(myCorpus, content_transformer(tolower))
```

> \textit{what does your phrase "17 pieces of tahitian south sea pearl" mean? i am very interested in this necklace - is this your best price?}

  ### Removing punctuation:
  
  
  Since computer cannot actually read meaning of punctuations. Punctuation and other special characters only look like more words to the computer and R. Use the following to methods to remove them from the text. 
  
  In some cases, if necesasry, such as when working with emails, we can also remove special characters.This list has been customized to remove punctuation that you commonly find in emails. You can customize what is removed by changing them as you see fit, to meet your own unique needs.

```{r}

```



